---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# memorids

The goal of memorids is to provide a simple way to get good quality, memorable IDs.

<!-- badges: start -->
[![R-CMD-check](https://github.com/sellorm/memorids/workflows/R-CMD-check/badge.svg)](https://github.com/sellorm/memorids/actions)
[![Codecov](https://img.shields.io/codecov/c/github/sellorm/memorids.svg)](https://codecov.io/gh/sellorm/memorids/)
<!-- badges: end -->


For one reason or another I've implemented various versions of this over the years and wanted to make a simple, reusable package to do the work for me instead.

The IDs created are two words in English -- an adjective followed by a noun -- and are built from a random sample of a list of each.

memorids has enough adjectives and nouns to create over half a million unique combinations of ID.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

```{r, eval=FALSE}
# install.packages("devtools")
devtools::install_github("sellorm/memorids")
```

## Example

Let's set a seed first so the results are reproducible:

```{r}
set.seed(42)
```


memorids offers a single function, `memorid()`, which returns a random memorable ID.

```{r}
memorids::memorid()
memorids::memorid()
memorids::memorid()
```

You can also change the separator.

```{r}
memorids::memorid(sep = " ")
```

## Collisions

Please remember that memorids aren't unique IDs. There are a finite number of them -- `r format(memorids:::num_combinations(), big.mark=",")` to be precise -- and as a consequence, you should not use them in situations where a unique ID is required without also checking for collisions.

The safest way to do this is to track what memorids you're currently using and check against that list for a collision when issuing a new memorid.

```{r}
memorids:::memorids_stats()
```

## pre-commit hook

The repo contains a handy pre-commit hook to prevent committing when either `data-raw/nouns.txt` or `data-raw/adjectives.txt` is newer than `R/sysdata.R`.

To use it run the following in the main `memorid` directory:

```{bash, eval=FALSE}
ln -s ../../pre-commit.R .git/hooks/pre-commit
```
